On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-01-03 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Add the proof for Lemma 4.4 (ex Lemma 2.7)
Review 2, medium remark 5
[J220] Put the references in alphabetical order or authors
As was requested by the Editor

\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

@@

>>>>

\usepackage[backend=biber,style=gost-numeric,sorting=nyt]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

@@

\begin{proof}
	Suppose the contrary.
	Then $AC$ in the minimal side of the triangle $ABC$ and, thus, the angle $ABC$ is acute.
	So are also angles $BCD$, $CDA$ and $DAB$.
	We conclude that all angles of a convex quadrilateral $ABCD$ are acute, which is impossible.
	The contradiction concludes the proof.
\end{proof}
